Placeholder

### 2021-02-05 Paper_Histograms.Rmd
Copy and pasted impute chunks into hisograms script from final analyses check notebook script

>>>>

# Set up

```{r read in data }

# Read in data
library(knitr)
library(summarytools)
library(psych)
library(polycor)
library(corrplot)
library(patchwork)
library(broom)
library(tidyverse)
library(ggpubr)

# get file info
source("../PANCHANGE_raw_path.R")

alldat <-  readRDS(file = paste0(data_path, "/four_cohorts_variables_exclusion.rds"))

```

# Impute and subset data

Impute retrospective scores if no change reported

```{r impute retro}

# impute retro for those who did not change

alldat$gad.sum_score_retro <- ifelse(alldat$gad.pandemic_felt_feelings == "No different", alldat$gad.sum_score_base,alldat$gad.sum_score_retro)
alldat$phq.sum_score_retro <- ifelse(alldat$phq.pandemic_felt_feelings == "No different", alldat$phq.sum_score_base,alldat$phq.sum_score_retro)
```

subsample for retro-baseline analysis
exclude those who do not have complete responses for both baseline and retrospective
in addition to those already excluded for NA in age, gender and MH diagnosis.

RETROSPECTIVE
```{r subset retrospective data }
dat.retro <- alldat %>%
  filter(
    ((data_group_gad == "Baseline and retrospective data" |
        data_group_gad == "All prepandemic, baseline and retrospective data") |
       (data_group_phq == "Baseline and retrospective data" |
          data_group_phq == "All prepandemic, baseline and retrospective data") |
        (data_group_pcl == "Baseline data only" |
           data_group_pcl == "Baseline and retrospective data" |
            data_group_pcl == "Prepandemic and baseline data" |
      data_group_pcl == "All prepandemic, baseline and retrospective data"))
  )

dim(dat.retro)
```

subsample for prepan-baseline analysis
exclude those who do not have complete responses for both baseline and prepandemic
in addition to those already excluded for NA in age, gender and MH diagnosis.

PREPANDEMIC
```{r subset prepandemic}

dat.prepan <- alldat %>%
  filter(
    ((data_group_gad == "Prepandemic and baseline data" |
        data_group_gad == "All prepandemic, baseline and retrospective data") |
       (data_group_phq == "Prepandemic and baseline data" |
          data_group_phq == "All prepandemic, baseline and retrospective data") |
       (data_group_pcl == "Prepandemic and baseline data" |
          data_group_pcl == "All prepandemic, baseline and retrospective data") ) &
      prepandemic_march_1_numeric == 1 # Exclude participants that signed up after the 1. March
  )

dim(dat.prepan)

```

Subset by study

```{r subset by study}

## Subset samples by study

GLAD.prepan <- dat.prepan %>%
  filter(Sample == "GLAD" | 
           Sample == "EDGI")

NBR.prepan <- dat.prepan %>%
  filter(Sample == "NBR")

RAMP.prepan <- dat.prepan %>%
  filter(Sample == "RAMP")

### retro
GLAD.retro <- dat.retro %>%
  filter(Sample == "GLAD" | 
           Sample == "EDGI")

NBR.retro <- dat.retro %>%
  filter(Sample == "NBR")

RAMP.retro <- dat.retro %>%
  filter(Sample == "RAMP")

```
